Parallel Tractability of Ontology\\ Materialization: Technique and Practice

### 2018-02-27 parallel-tractability-J-v9/response.tex

\begin{quote}
It would be much better if the ontology names corresponded to the example
numbers, i.e., the ontology in Example 6 was Oex6.
\end{quote}

We made the ontology subscripts correspond to the example numbers
for Example~5, Example~6, Example~7 and Example~9.

\begin{quote}
The notion of a simple concept is very much tied to the algorithm developed
in the paper.  How often do actual ontologies have constructs that could
make them intractable that are rended tractable by having simple concepts?
If there are none, then this class is uninteresting, particularly as the
paper makes such strong claims about worrying about particular ontologies.
This is different from an ontology only containing simple concepts.
\end{quote}

We investigated real ontologies from different data sources. These ontologies cover
several domains and only contain simple concepts (these ontologies can be
obtained from the address given in the last paragraph of
Section~6.1).\\

@@

\begin{quote}
Figure 5 is very misleading because it uses different scales for the two
systems.   There are several immediate questions that arise from this Figure
that are poorly handled in the paper.  First, why does going from one thread
to two make such a difference for ParallelDHL?  Without a convincing
explanation for this surprising aspect of the benchmarking it is hard to
trust any of the rest of the benchmarking.  The other surprising aspect of
Figure 5 is that RDFox speeds up so little.  There is a short explanation of
why this is so, but I would have liked to see a longer one.
\end{quote}

In the original experiments, ParallelDHL required a large amount of time for computing
the relation $S_{\textit{\!\tiny rch}}$ when only one thread is being allocated.
With several threads allocated, ParallelDHL has a better efficiency.
This also resulted in the difference of the speedups between RDFox and ParallelDHL.

\begin{quote}
The computation of the speedup numbers is wholely unexplained.  Why should
this number have any importance?
\end{quote}

We used the speedup numbers to show the different performance for
ontologies in $\mathcal{D}_{\textit{\text{dhl}}(\circ)}$ and those
 not in $\mathcal{D}_{\textit{\text{dhl}}(\circ)}$.\\

@@

In the revision, we provide the formula for the speedup and analyze
the speedup numbers.

\begin{quote}
There is a claim that the benchmarking distinguishes between the Ddhlo and
D-dhlo.  However, Figure 5 doesn't really show this well, if at all.   For
example, why should processing slow down with more threads at all?  Further,
it appears that even for several of the more well-behaved ontologies that there
is very little speedup between 6 and 8 processors.
\end{quote}

ParallelDHL is mainly
optimized based on the graph depth. Thus, when the graph depth is the
dominant factor that determines the reasoning time, the experiment 
should have a better performance. 
In the original experiments, the eight ontologies were used to make
the experiments close to real-world scenarios.
Since the graph depths of different ontologies affect the reasoning times
to different degrees, the experimental results are not very clear
to explain the issue of parallel tractability.
This is also why
Figure 5 does not show the differences between the ontologies in
$\mathcal{D}_{\textit{\text{dhl}}(\circ)}$ and those not in
$\mathcal{D}_{\textit{\text{dhl}}(\circ)}$ well.\\

In order to make the graph depth a dominant factor, we modified the LUBM benchmark to 
generate ontologies of different graph depths and conducted the new experiments
in the revision.
